\chapter{Introduction}

\section{Welcome to the MEGA65!}

Congratulations on your purchase of one of the most long-awaited computers in the history of computing. The MEGA65 is a community designed computer, based on the never-released Commodore{\textregistered} 65\footnote{Commodore is a trademark of C= Holdings} computer, a computer designed in 1989 and intended for public release in 1990. Now, decades later, the MEGA65 invokes a time when computers were simple and friendly. They were not only easy to operate and understand, but friendly and approachable for new users.

These 1980s computers inspired an entire generation to choose the exciting and rewarding careers they have today. Just imagine the joy of these individuals as they discovered that they could use their new computer to write a letter, prepare taxes, invent new things, or even learn about how the universe works. We want to re-create that level of excitement, which is rarely found in modern computing. So we made the {\bf MEGA65}.

The MEGA65 team believes that owning a computer is like owning a home. You don't just buy a home and move in, you change things big and small to make it your own custom living space. After settling in, you may decide to renovate or extend your home to make it more comfortable or provide more utility. Think of the MEGA65 as a "computing home".

This guide will teach you how to do more than just hang pictures on a wall, it will help you build your dream home. You will learn how to operate the MEGA65, code programs, add additional software, and extend the hardware capabilities. You will also learn about the history of computing as you discover the MEGA65's operating system commands and explore BASIC version 65.

Computer graphics and music make computing more fun; and we designed the MEGA65 for fun! In this user's guide, you
will learn to code using the MEGA65's built-in {\bf graphics} and {\bf sound} capabilities. But you don't need to be
a programmer to have fun with the MEGA65. Because the MEGA65 includes a complete Commodore{\textregistered}
64{\texttrademark}\footnote{Commodore 64 is a trademark of C= Holdings,}, it can run thousands of games, utilities
and business software from the past, and new programs being written today by Commodore computer enthusiasts.
Excitement for the MEGA65 will grow as programmers test the limits of this modern Commodore computer recreation.
Together, we will build a new "home-brew" community to create software--------------------------------- that no one
ever thought was possible on
the MEGA65.

We welcome you on this journey! Thank you for becoming a part of the {\bf MEGA65}
community of users, programmers, and enthusiasts! Get involved, learn more
about your MEGA65, and join us online at:

% I thought a call to action to join the community would be good to add early on. Where will the final online community call home?

\section{Other Books in this series}

This is one of several MEGA65 documentation volumes.  The series includes:

\begin{itemize}
	\item The MEGA65 User Guide -- Provides an introduction to the MEGA65, and a condensed BASIC 65 command reference
	\item The MEGA65 BASIC 65 Reference Guide -- Comprehensive documentation of all BASIC 65 commands, functions and operators
	\item The MEGA65 Chipset Reference -- Detailed documentation about the MEGA65 and C65's custom chips
	\item The MEGA65 Developer Guide -- Information for developers who wish to write programmes for the MEGA65
	\item The MEGA65 Book -- All volumes in a single huge PDF for easy online searching. 1080 pages and growing!
\end{itemize}
